---
title: "Syllabus"
author: Giuliano Colosimo
date: "`r Sys.Date()`"
bibliography: /Users/giulianocolosimo/Dropbox/manuscripts/literature/bibtex/comprehensive_database.bib
csl: /Users/giulianocolosimo/Dropbox/manuscripts/literature/bibtex/apa_5th_edition.csl
citation_package: biblatex
citecolor: "red"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```

## General information

This is an discretionary course for master level students enrolled in the "Biologia Evoluzionistica, Ecologia e Antropologia Applicata" degree at the University of Rome Tor Vergata. It is worth **2 CFU** for a total of 16 hours to be administered in person (or remotely, depending on the evolution of the pandemic) during the second semester of academic year 2022/2023.


|          | Day       | Time           | Location                |
|----------|-----------|----------------|-------------------------|
| Lectures | Friday    | 11:00 - 13:00  | AULA Centro Studi Pesca |
| Final exam           | TBD       | 11:00 - 13:00 | AULA Centro Studi Pesca |


::: callout-note
As attendance is mandatory I will work with enrolled students to find the best time and day so that all can follow the class in person! 
:::


```{r aula, echo=FALSE}
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng = 12.62825, lat = 41.85024, popup="AULA Centro Studi Pesca")
```


## Course language

The course will be thought in Italian unless international students are present. In this latter case the course will be thought in English. All the material and the literature used (including this website!) will be in English.

## Pre-requisites

This is an introductory course, so no prior knowledge of this topic is required. Throughout the course students will be extensively exposed to various software and web-tools. All software used is freely available and relatively easy to install. It is necessary that each student has his/her own laptop in order to better follow the various demonstrations/exercises that will take place in class. Problem-solving skills and a good knowledge of your own computer OS structure and function will definitely be useful.

This course does not teach you system administration skills and you should know how to read help files and software guides, as well as retrieve information on-line. Should a student not have a portable computer, all code, demonstrations, and class slides will be uploaded on this website and are available for practice on a desktop computer.

::: callout-warning
Note that the code has been written on a Unix-based systems (macOS). That being said, the material covered in class should work fine on Windows systems as well!
:::

## Textbook

As this is an introductory and discretionary course there is no textbook and most of the readings you will be doing is based on peer-reviewed manuscripts published on various scientific journals. Still, if you are really interested in this topic a really good and detailed book is @Guisan2020.

## Additional Resources

As this course will heavily rely on the use of R and R-Studio I am adding here some very useful resources that I encourage to use.

-   [CRAN](https://cran.r-project.org)
-   [StackOverflow](https://stackoverflow.com)
-   [Bioconductor](http://www.bioconductor.org)
-   [Un Viaggio nell'Ambiente R](https://tommaso-russo.github.io/libroR/index.html)

## Learning objectives

The course aims to train the student in the techniques of acquisition, organization and analysis of data for the long-term tracking of animals in the field of Conservation Biology. The course offers an overview of the different types of marking and tracking of wildlife, and promotes an understanding of their best ways of use in relation to the specific field of application. Through the review of the scientific literature and the discussion of the different animal monitoring techniques, the course participants will develop the necessary critical skills for understanding the various problems related to the acquisition and organization of time series of data for animal tracking.

## Class evaluation

At the end of the course, students will be evaluated with a written exam.

### Participation to class and discussion

We will be reading and discussing primary literature on Movement Ecology. The critical comparison of the various methodologies of data acquisition, organization and processing will constitute the basis for the formulation of the student's final judgment. Aspects that will be used to assess students' learning level are their participation and interaction during the course and their ability to present and discuss scientific literature articles.


## Meeting hours

Each student is welcome and encouraged to contact me by e-mail with questions and doubts. My office hours are between 10:00 and 12:00 every Wednesday. My office is number 14, located on the first floor of the main building at "Laboratori di Ecologia Sperimentale ed Acquacoltura". 

::: callout-tip
It is always a good idea to e-mail me before coming to the office, to prevent overcrowding.
:::

## Students with disabilities

Please, let me know if you require special accommodations to follow this class.

# References
